### 2011-11-06 doc/pldi2012/mapping_fig.tex
several figures done - references linked up

\begin{figure}[t]
  \centering
  \subfigure[mapping of $dc_0$ task]{
    \label{sfig:mapping_fig:dc}
    \begin{tikzpicture}
      \partitiontree
    \end{tikzpicture}
  }
  \subfigure[mapping of $volt_0$ task]{
    \label{sfig:mapping_fig:volt}
    \begin{tikzpicture}
      \partitiontree
    \end{tikzpicture}
  }
  \subfigure[mapping completed]{
    \label{sfig:mapping_fig:done}
    \begin{tikzpicture}
      \partitiontree
    \end{tikzpicture}
  }
  \label{fig:mapping_fig}
  \caption{Mapping of tasks in region tree -- TODO: draw in little boxes and stuff}
\end{figure}

>>>>

\usetikzlibrary{calc}
\begin{figure}[t]
  \centering
  \subfigure[mapping of $cnc_0$ task]{
    \label{sfig:mapping_fig:cnc}
    \begin{tikzpicture}
      \partitiontree
      \node(cnc_p0)[very thick,draw,fill=white] at (0.45,0.30) {\tiny $cnc_0$};
      \node(cnc_g0)[very thick,draw,fill=white] at (5.45,0.30) {\tiny $cnc_0$};
      \node(def_top)[very thin,draw,fill=white] at (3.3,4.35) {\tiny ~~---~~};
      \draw[very thick] ($ (top.south)!.5!(ptp.center) $) circle (2pt);
      \draw[very thick] ($ (pvsf.north)!.5!(ptf.center) $) circle (2pt);
      \draw[very thick] ($ (pvsf.250)!.5!(ppp.center) $) circle (2pt);
      \draw[very thick] ($ (p0.north)!.5!(pp0.center) $) circle (2pt);
      \draw[very thick] ($ (pvst.north)!.5!(ptt.center) $) circle (2pt);
      \draw[very thick] ($ (pvst.310)!.5!(pgp.center) $) circle (2pt);
      \draw[very thick] ($ (g0.north)!.5!(pg0.center) $) circle (2pt);
      \draw[very thick,->] (def_top) to [bend right=45] (cnc_p0);
      \draw[very thick,->] (def_top) to [bend left=45] (cnc_g0);
    \end{tikzpicture}
  }
  \subfigure[mapping of $dc_0$ task]{
    \label{sfig:mapping_fig:dc}
    \begin{tikzpicture}
      \partitiontree
      %\node(cnc_p0)[very thick,draw,fill=white] at (0.45,0.30) {\tiny $\begin{array}{c}\cancel{cnc_0} \\ dc_0\end{array}$};
      \node(dc_p0)[very thick,draw,fill=white] at (0.45,0.30) 
{\tiny
$\begin{array}{@{}c@{}}
\cancel{cnc_0} \\
dc_0
\end{array}$};
      \node(cnc_p1)[very thin,draw,fill=white] at (1.25,0.30) {\tiny $cnc_1$};
      \node(cnc_pn)[very thin,draw,fill=white] at (2.25,0.30) {\tiny $cnc_{n-1}$};
      \node(cnc_g0)[very thin,draw,fill=white] at (5.45,0.30) {\tiny $cnc_0$};
      \node(dc_g0)[very thick,draw,fill=white] at (5.45,0.75) {\tiny $dc_0$};
      \draw[very thick,->] (cnc_g0.west) to [bend left=70] (dc_g0.west);
      \draw[very thick] ($ (cnc_g0.center) - (0.25,0.25) $) -- ++(0.5,0.5);
      \draw[very thick] ($ (cnc_g0.center) - (0.25,-0.25) $) -- ++(0.5,-0.5);
      \node(cnc_g1)[very thin,draw,fill=white] at (6.25,0.30) {\tiny $cnc_1$};
      \node(cnc_gn)[very thin,draw,fill=white] at (7.25,0.30) {\tiny $cnc_{n-1}$};
      \node(def_top)[very thin,draw,fill=white] at (3.3,4.35) {\tiny ~~---~~};
      \draw[very thin] ($ (top.south)!.5!(ptp.center) $) circle (2pt);
      \draw[very thin] ($ (pvsf.north)!.5!(ptf.center) $) circle (2pt);
      \draw[very thin] ($ (pvsf.250)!.5!(ppp.center) $) circle (2pt);
      \draw[very thin] ($ (p0.north)!.5!(pp0.center) $) circle (2pt);
      \draw[very thin] ($ (p1.north)!.5!(pp1.center) $) circle (2pt);
      \draw[very thin] ($ (pn.north)!.5!(ppn.center) $) circle (2pt);
      \draw[very thin] ($ (pvst.north)!.5!(ptt.center) $) circle (2pt);
      \draw[very thin] ($ (pvst.310)!.5!(pgp.center) $) circle (2pt);
      \draw[very thin] ($ (g0.north)!.5!(pg0.center) $) circle (2pt);
      \draw[very thin] ($ (g1.north)!.5!(pg1.center) $) circle (2pt);
      \draw[very thin] ($ (gn.north)!.5!(pgn.center) $) circle (2pt);
    \end{tikzpicture}
  }
  \subfigure[mapping of $volt_0$ task]{
    \label{sfig:mapping_fig:volt}
    \begin{tikzpicture}
      \partitiontree
      \node(dc_p0)[very thin,draw,fill=white] at (0.45,0.30) {\tiny $dc_0$};
      \node(dc_p1)[very thin,draw,fill=white] at (1.25,0.30) {\tiny $dc_1$};
      \node(dc_pn)[very thin,draw,fill=white] at (2.25,0.30) {\tiny $dc_{n-1}$};
      \node(dc_g0)[very thin,draw,fill=white] at (5.45,0.30) {\tiny $dc_0$};
      \node(volt_p0)[very thick,draw,fill=white] at (0.45,0.75) {\tiny $volt_0$};
      \draw[very thick,->] (dc_p0.west) to [bend left=70] (volt_p0.west);
      \draw[very thick] ($ (dc_p0.center) - (0.25,0.25) $) -- ++(0.5,0.5);
      \draw[very thick] ($ (dc_p0.center) - (0.25,-0.25) $) -- ++(0.5,-0.5);
      \draw[very thick] ($ (dc_g0.center) - (0.25,0.25) $) -- ++(0.5,0.5);
      \draw[very thick] ($ (dc_g0.center) - (0.25,-0.25) $) -- ++(0.5,-0.5);
      \node(dc_g0)[very thin,draw,fill=white] at (5.45,0.30) {\tiny $dc_0$};
      \node(dc_g1)[very thin,draw,fill=white] at (6.25,0.30) {\tiny $dc_1$};
      \node(dc_gn)[very thin,draw,fill=white] at (7.25,0.30) {\tiny $dc_{n-1}$};
      \draw[very thick] ($ (dc_g0.center) - (0.25,0.25) $) -- ++(0.5,0.5);
      \draw[very thick] ($ (dc_g0.center) - (0.25,-0.25) $) -- ++(0.5,-0.5);
      \draw[very thick] ($ (dc_g1.center) - (0.25,0.25) $) -- ++(0.5,0.5);
      \draw[very thick] ($ (dc_g1.center) - (0.25,-0.25) $) -- ++(0.5,-0.5);
      \draw[very thick] ($ (dc_gn.center) - (0.25,0.25) $) -- ++(0.5,0.5);
      \draw[very thick] ($ (dc_gn.center) - (0.25,-0.25) $) -- ++(0.5,-0.5);
      \node(def_top)[very thin,draw,fill=white] at (3.3,4.35) {\tiny ~~---~~};
      \draw[very thin] ($ (top.south)!.5!(ptp.center) $) circle (2pt);
      \draw[very thin] ($ (pvsf.north)!.5!(ptf.center) $) circle (2pt);
      \draw[very thin] ($ (pvsf.250)!.5!(ppp.center) $) circle (2pt);
      \draw[very thin] ($ (p0.north)!.5!(pp0.center) $) circle (2pt);
      \draw[very thin] ($ (p1.north)!.5!(pp1.center) $) circle (2pt);
      \draw[very thin] ($ (pn.north)!.5!(ppn.center) $) circle (2pt);
      \draw[very thin] ($ (pvst.north)!.5!(ptt.center) $) circle (2pt);
      \draw[very thin] ($ (pvst.310)!.5!(pgp.center) $) circle (2pt);
      \draw[very thin] ($ (g0.north)!.5!(pg0.center) $) circle (2pt);
      \draw[very thin] ($ (g1.north)!.5!(pg1.center) $) circle (2pt);
      \draw[very thin] ($ (gn.north)!.5!(pgn.center) $) circle (2pt);
      \draw[very thick] ($ (g0.north)!.5!(pg0.center) - (0.1,0.1) $) -- ++(0.2,0.2);
      \draw[very thick] ($ (g0.north)!.5!(pg0.center) - (0.1,-0.1) $) -- ++(0.2,-0.2);
      \draw[very thick] ($ (g1.north)!.5!(pg1.center) - (0.1,0.1) $) -- ++(0.2,0.2);
      \draw[very thick] ($ (g1.north)!.5!(pg1.center) - (0.1,-0.1) $) -- ++(0.2,-0.2);
      \draw[very thick] ($ (gn.north)!.5!(pgn.center) - (0.1,0.1) $) -- ++(0.2,0.2);
      \draw[very thick] ($ (gn.north)!.5!(pgn.center) - (0.1,-0.1) $) -- ++(0.2,-0.2);
      \draw[very thick] ($ (pvst.310)!.5!(pgp.center) - (0.1,0.1) $) -- ++(0.2,0.2);
      \draw[very thick] ($ (pvst.310)!.5!(pgp.center) - (0.1,-0.1) $) -- ++(0.2,-0.2);
      \draw[very thick] ($ (pvst.230)!.5!(psp.center) $) circle (2pt);
      \draw[very thick] ($ (s0.north)!.5!(ps0.center) $) circle (2pt);
      \node(def_pvst)[very thick,draw,fill=white] at (5.3,2.75) {\tiny ~~---~~};
      \draw[very thick,->] (dc_g0.north) to [bend right=30] (def_pvst.270);
      \draw[very thick,->] (dc_g1.north) to [bend right=30] (def_pvst.315);
      \draw[very thick,->] (dc_gn.north) to [bend right=30] (def_pvst.0);
      \node(volt_s0)[very thick,draw,fill=white] at (3.2,0.30) {\tiny $volt_0$};
      \draw[very thick,->] (def_pvst.190) to [bend right=40] (volt_s0.130);
    \end{tikzpicture}
  }
  \label{fig:mapping_fig}
  \caption{Mapping of tasks in region tree}
\end{figure}
